\section{Software architecture}

\subsection{ROS} Robot operating system \cite{ROS} is an open-source software which serves as middleware for robotic software development across many platforms. ROS offers a flexible framework of numerous libraries, software tools for communication, motion planning, navigation, localization and mapping and for robust robotic software development. ROS supports many programming languages including C++, Python, Matlab, etc. A modular and distributed software platform along with a vibrant user community all over the world makes ROS very popular among roboticists, students and researchers. In this project, communication between camera and robot are implemeted by exploiting ROS features like publishers and subscibers and visualization tool Rviz has been employed effectively.

\subsection{Open3D} 
Open3D \cite{open3d} is an open-source library loaded with set of tools for 3D data processing such as scan matching (ICP), point cloud visualisation, RGBD image based odometry, etc. Open3D supports development using C++ and Python programming languages. In this thesis, ICP scan registration and point cloud visualization is implemented using open3D.   

\subsection{miniSam}
miniSam \cite{miniSam} is an open-source library which provides factor graph based framework to solve non-linear least square optimization problem. While front-end of miniSam supports c++ and python prgramming languages, back-end is higly optimised for efficient computation. The task of pose-graph creation and optimization has been efficiently used in this thesis work.  

\subsection{Scikit-learn}
Scikit-learn \cite{scikit-learn} is a open-source python based machine learning framework that supports classification, Regression, Clustering, Dimensionality reduction, etc. Scikit-learn offers variuos alogirthms for cluster processing such as K-Means, DBSCAN, etc. Scikit-learn is mainly used for cluster processing.   



